### 2012-05-10 trunk/GUIErrorDetector/paper/technique.tex
small tweak

\noindent  {\textsc{\textbf{Problem.}}}
At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI-accessing method.

>>>>

\noindent  {\textsc{\textbf{Problem.}}}
At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI-accessing method.\vspace{1mm}

\noindent  {\textsc{\textbf{Example.}}} Figure~\ref{fig:simplecg} shows an example call graph
to illustrate the invalid thread access problem.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.40]{simplecg}
  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
invalid thread access problem. The \CodeIn{entry()} node is executing
in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
indicates an invalid thread access error.}}
\vspace{-2mm}
\end{figure}
